Comparative Analysis of Legislative Complex Networks of Select North American and European Countries

### 2018-12-11 paper/paper.tex
editing methods
adding graphing_trends
adding average trends across countries

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship. We found summary statistics for each of the countries and plotted different centrality measures for comparison.
    % To-do: Finish abstract %
\end{abstract}

@@

\section{Methods}

\subsection{Data Collection and Pre-Processing}
We first obtained cosponsorship data for the countries: Austria, Denmark, France, Sweden, Switzerland, United Kingdom, and the United States. This was taken taken from the following resources: \underline{Bill cosponshorship} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{US Congress} \cite{US}. The raw data was parsed and saved as \texttt{graphml} files. Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing. The data is stored in \texttt{CSE-416-Final-Project/data/} in our repository.

\subsection{Data Analysis}
We created a function

\section{Results and Discussion}

>>>>

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship. We found and plotted summary statistics and centrality measures to make comparisons possible.
    % To-do: Finish abstract %
\end{abstract}

@@

\section{Materials and Methods}

\subsection{Data Collection and Pre-Processing}
We first obtained cosponsorship data for the countries: Austria, Denmark, France, Sweden, Switzerland, United Kingdom, and the United States. This was taken taken from the following resources: \underline{Bill cosponshorship} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{US Congress} \cite{US}. The raw data was parsed and saved as \texttt{graphml} files. Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing. The data is stored in \texttt{CSE-416-Final-Project/data/} and the pre-processing was performed in the \texttt{Analysis} file in the root directory within our repository.

\subsection{Data Analysis}

\section{Results}

\section{Discussion}
